---
title: "Collector Behavior"
author: "Kelley Erickson"
date: "10/14/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

## Data filtering
Data filter                     | Definition
-------------                   | -------------
**Species filter**              | Collectors who have collected species _i_ at least once
**Genus breadth filter**        | collectors who have collected more than one genus (as well as collectors who have only collected plants within the genus of species _i_
**Family breadth filter**       | collectors who have collected more than one family (as well as collectors who have only collected Anacardiaceae)
**Phenology filter**            | collectors who have collected in the same months as species _i_ has been collected
**Invasive filter**            | collectors who have collected at least one invasive species

## Occurrences by Species  {.smaller}

Species  |  Common Name |  Status |  Unique Collectors | Counties | Total GBIF records (FL) | Records after cleaning 
--- | --- |--- | --- | --- | --- | ---
_Mangifera indica_ | Mango | Introduced | 38 | 13 | 95 | 44
_Metopium toxiferum_ | Poisonwood | Native | 98 | 6 | 160 | 119
_Rhus aromatica_ | Fragrant Sumac | Native | 3 | 1 | 4 | 3
_Rhus copallinum_ | Winged Sumac | Native | 207 | 57 | 336 | 296
_Rhus glabra_ | Smooth Sumac | Native | 5 | 6 | 10 | 7
_Rhus michauxii_ | Michaux's Sumac | Native, Endangered | 1 | 1 | 1 | 1

(continued on next slide)

## Occurrences by Species (continued) {.smaller}
Species  |  Common Name |  Status |  Unique Collectors | Counties | Total GBIF records (FL) | Records after cleaning 
--- | --- |--- | --- | --- | --- | ---
_Schinus terebinthifolia_ | Brazilian Pepper | Invasive | 324 | 36 | 610 | 495
_Sorindeia madagascariensis_ | Mtikiza | Introduced | 1 | 1 | 4| 1
_Spondias purpurea_ | Purple Mombin | Introduced | 12 | 3 | 16 | 13
_Toxicodendron pubescens_ | Eastern Poison Oak | Native | 30 | 32 | 42 | 36
_Toxicodendron radicans_ | Eastern Poison Ivy | Native | 269 | 58 | 415 | 379
_Toxicodendron vernix_ | Poison Sumac | Native | 34 | 21 | 59 | 46

## Slide with R output
```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

